A Topography of Climate Change Research

### 2018-07-26 pres/CC_Topography_EASST_Callaghan.tex
update presentation

\begin{frame}{Introduction}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\begin{figure}
				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item<2-> Topography is a description of a landscape
				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of body of text
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\end{frame}

@@

\only<3->{
\textbf{Steps}
\begin{enumerate}
\item<4-> Download documents from Web of Science (WoS)
\item<5-> Match documents to reference lists from IPCC reports
\item<6-> Topic model stemmed document abstracts
\end{enumerate}
}
\end{frame}

>>>>

\begin{frame}{Introduction}
\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}
			\begin{figure}
				\includegraphics[width=1\linewidth]{../plots/Hondius_Portrait_of_map-makers}
				\caption{Portrait of map-makers, Gerard Mercator and Jodocus Hondius (Jodocus Hondius) source: \url{https://commons.wikimedia.org/wiki/File:Hondius_Portrait_of_map-makers.jpg}}
			\end{figure}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item<2-> Topography is a description of a landscape
				\item<3-> Topics (from the Greek \texttau\textomikron\textpi\textomikron\textvarsigma, place) can describe the features of a body of text
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\end{frame}

@@

\only<3->{
\textbf{Steps}
\begin{enumerate}
\item<4-> Download document metadata from Web of Science (WoS)
\item<5-> Match documents to reference lists from IPCC reports
\item<6-> Topic model stemmed document abstracts
\end{enumerate}
}
\end{frame}
